Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A study based on the parametric g-formula

### 2024-04-10 output/paper/manuscript.qmd
Added title page. Updated text for results effect modification since different.

@Tbl-hypothesis-1and2 presents the results of the difference between estimates of the {{< acr mcs >}} on the logarithmic scale for females and males, for the {{< acr edcs >}} on the glucocorticosteroids and {{< acr hitrtse >}}. For {{< acr hitrtse >}}, significant differences were present for the phenol OXBE (`r format_res(heffects1, "oxbe", "HRT-SE")`) and the phthalate metabolites MEP (`r format_res(heffects1, "mep", "HRT-SE")`) and MbZP (`r format_res(heffects1, "mbzp", "HRT-SE")`). For the glucocorticosteroids, significant differences were present across all three classes of {{< acr edcs >}} and for all outcomes. The largest differences were attributable to the {{< acr opps >}} DMTP (cortisol production, `r format_res(heffects2, "dmtp", "cortisol production")`) and DETP (corticosterone production, (`r format_res(heffects2, "detp", "corticosterone production")`); cortisone production, (`r format_res(heffects2, "detp", "cortisone production")`)). The forest plots of the individual {{< acr mcs >}} are presented in Supplementary Figures [-@suppfig-marginal-1sa] and [-@suppfig-marginal-2sa].

>>>>

@Tbl-hypothesis-1and2 presents the results of the difference between estimates of the {{< acr mcs >}} on the logarithmic scale for females and males, for the {{< acr edcs >}} on the glucocorticosteroids and {{< acr hitrtse >}}.
For {{< acr hitrtse >}}, significant differences were present for the phenol OXBE (`r format_res(heffects1, "oxbe", "HRT-SE")`) and the phthalate metabolite MbZP (`r format_res(heffects1, "mbzp", "HRT-SE")`).
For the glucocorticosteroids, significant differences were present across all three classes of {{< acr edcs >}} and for all outcomes. The largest differences were attributable to the phenol ETPA (corticosterone production, `r format_res(heffects2, "etpa", "corticosterone production")`) and the phthalate metabolite MEHP (cortisol production, (`r format_res(heffects2, "mehp", "cortisol production")`); cortisone production, (`r format_res(heffects2, "mehp", "cortisone production")`)). The forest plots of the individual {{< acr mcs >}} are presented in Supplementary Figures [-@suppfig-marginal-1sa] and [-@suppfig-marginal-2sa].
